\sysfull

### 2017-08-11 paper/evaluation.tex
Revisions on evaluation section: results added

We present the experimental results of \sys's performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

@@

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Bitcount & 351 & 588 \\ %59\%
		Cold chain & 388 & 721 \\ %53\%
		Cuckoo & 483 & 762 \\ %63\%
		RSA & 887 & 1233 \\ %71\%
		DFT & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		Huffman & {} & {} \\ %Data decompression size: 100 bytes
		Selection sort & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

@@

%\vspace{2cm}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{Performance of \sys's  tasks coalescing mechanism compared to virtual task size equal to one (per application) at multiple WISP to RFID reader antenna distances.\todo{Replace "coal" with "coalescing", "No-coal" with "No coalescing"; use markers in addition to color; decide on uniform naming for apps (either all small or capitalized)}{Amjad}}
	\label{fig:coalescing}
\end{figure}

@@

\subsubsection{\sys Compiler Overhead}
\label{sec:result_compiler time}

\begin{figure}
	\centering
	%\includegraphics[width=\columnwidth]{figures/}
	\caption{\sys compiler overhead.}
	\label{fig:coalescing}
\end{figure}

\subsubsection{Virtual Task Size}
\label{sec:result_task_size}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average virtual task size (measured in real task unit\todo{Define real task unit}{Amjad}) of the virtual task sizes that the coalescing algorithm used to accomplished the applications at a WISP to RFID reader distance of 60\,cm.\todo{Please rewrite this sentence}{Amjad}}
	\label{fig:aveVirtuTaskSize}
\end{figure}

@@

%\subsubsection{Completion Time}
%\label{sec:result_completion}

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/chain_vipe}
%	\caption{Time to complete for a set of testing applications (refer to Table~\ref{table:benchmark_list}) using \sys versus Chain (no coalescing applied, fixed power supply). \todo{Figure placeholder---will be replaced with final one}{Amjad}}
%	\label{fig:IPOSPerformance}
%\end{figure}

%Expected results:
%\begin{itemize}
%	\item performance for each application comparing bars for Chain, no coalescing/hand-tasked, coalescing/hand-tasked, no-coalescing/compiler, coalescing/compiler. Performance depicted, normalized to one of the configurations (probably Chain). This plot will cover most of the eval dimensions that we care about.
%	\item Sensitivity plot---show amount of task merged, time to completion, overhead (in terms of task-size/cap-size sweep (remember we can vary either with approximately the same effect)), energy consumed. All experiments for fixed power, at 3 distances with wireless power, compared against Chain for 3 task/cap size configurations
%\end{itemize}

%Point for decision after main figure is ready

%Pull the compiler stuff into its own plot that compares compiler to hand-tasked, maybe only for the coalescing fig.  This reduces bars in plot 1, but runs the risk of making the compiler sound secondary, which we do not want to do.

%*Report only Chain, coalescing/hand-tasked, coalescing/compiler in the main plot.  This says that coalescing is the "default configuration" for VIPER. Later, in a second figure, we compare coalescing to no coalescing for hand-tasked and compiler as a characterization plot.

%\todo{Provide results and text to this section}{Amjad}

\subsubsection{Memory Management Performance}
\label{sec:results_memory_management}

>>>>

%We present the experimental results of \sys's performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

@@

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Bitcount (bc) & 351 & 588 \\ %59\%
		Cold chain (cem) & 388 & 721 \\ %53\%
		Cuckoo (cuckoo) & 483 & 762 \\ %63\%
		RSA (rsa) & 887 & 1233 \\ %71\%
		Activity (ar) & 483 & 762 \\ %63\%
		DFT (dft) & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		Huffman (dd) & {} & {} \\ %Data decompression size: 100 bytes
		Selection sort (sort) & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_chain}
	\caption{Performance of \sys's fixed power and at multiple WISP to RFID reader antenna distances, \{20, 40, 60\}\,cm, compared against Chain.}
	\label{fig:coalescing}
\end{figure}

@@

\subsubsection{\sys Compiler Overhead}
\label{sec:result_compiler_time}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/comp_user}
	\caption{\sys compiler overhead measured per application.}
	\label{fig:comp_user}
\end{figure}

Result is provided in Figure~\ref{fig:comp_user}.

\subsubsection{\sys Coalescing Overhead}
\label{sec:result_compiler_time}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{\sys coalescing overhead measured per application.}
	\label{fig:coalescing}
\end{figure}

Result is provided in Figure~\ref{fig:coalescing}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average virtual task size.}
	\label{fig:aveVirtuTaskSize}
\end{figure}

@@

\subsubsection{\sys Paging Performance}
\label{sec:results_memory_management}
